\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{siunitx}
\usepackage{booktabs,array,tabularx}
\usepackage{ltablex} % makes tabularx break across pages
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}

\usepackage{array,booktabs,longtable}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
\setlength{\tabcolsep}{4pt}         % tighter columns (optional)
\renewcommand{\arraystretch}{1.12}  % a bit more row height (optional)


\sisetup{per-mode=symbol, exponent-product=\cdot}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1.15}

% --- ltablex settings ---
\keepXColumns  % keep X column widths across pages

% --- listings (XML) ---
\definecolor{codeline}{gray}{0.85}
\lstdefinestyle{xml}{
  language=XML,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue!60!black}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{green!40!black},
  showstringspaces=false,
  breaklines=true,
  frame=single,
  rulecolor=\color{codeline},
  xleftmargin=0.5em,
  xrightmargin=0.5em,
  aboveskip=0.6\baselineskip,
  belowskip=0.6\baselineskip,
  literate={ä}{{\"a}}1 {ö}{{\"o}}1 {ü}{{\"u}}1 {Ä}{{\"A}}1 {Ö}{{\"O}}1 {Ü}{{\"U}}1 {ß}{{\ss}}1 {°}{{$^\circ$}}1
}

% --- Wang (2009) notation ---
\newcommand{\uu}{\bm{u}}
\newcommand{\sig}{\bm{\sigma}}
\newcommand{\I}{\bm{I}}
\newcommand{\grad}{\nabla}
\newcommand{\divv}{\nabla\!\cdot}
\newcommand{\TT}{T}
\newcommand{\pp}{p}
\newcommand{\rhoW}{\rho_w}
\newcommand{\muW}{\mu}
\newcommand{\npor}{n}
\newcommand{\Sat}{S}
\newcommand{\alphaB}{\alpha_B}
\newcommand{\pcap}{p_c}
\newcommand{\vW}{\bm v^l}
\newcommand{\kperm}{\bm{k}}
\newcommand{\krel}{k_{\mathrm{rel}}(\Sat)}
\newcommand{\qW}{\bm{q}_w}
\newcommand{\qT}{\bm{q}_T}
\newcommand{\Ceff}{(\rho c)_r}
\newcommand{\keff}{k}

\title{Thermo--Richards--Mechanics (TRM)\\
\large Open-Geo-Sys model}
\author{MB}
\date{\today}

\begin{document}
\maketitle

\section{Link to paper}
This is summary of the configured OGS TRM model, rewritten into Wang–Kosakowski–Kolditz (2009) notation. 

Discussion goals:
\begin{itemize}
    
\item[(i)] confirm which couplings we actually switch on in OGS, and

\item[(ii)] see clearly how each XML parameter lands in the PDEs.

\end{itemize}

\section{Topics and issues to discuss in Leipzig (or earlier)}
The plan: based on provided data, present a model tuned for Bayesian inversion to determine
$\kperm$.
The current audit resolves the two formulation comments that were still open in the
first version of the notes:
\begin{itemize}
    \item \textbf{Homogeneity versus heterogeneity:} the exchanged OGS model remains a
    homogeneous-material TRM model.  The active workflow introduces heterogeneity only
    through run-local mesh-cell parameter fields, first for the intrinsic permeability
    tensor \(\kperm(\bm x)\).  Porosity and retention parameters are documented below
    as later releasable scalar options, but they are not part of the active objective
    until OGS state outputs and identifiability checks exist.
    \item \textbf{Specific expression for \(\krel\):} the XML uses
    \texttt{RelativePermeabilityVanGenuchten} with
    \(S_{\ell r}=0.1\), \(S_{gr}=0\), \(m=0.45\), and
    \(k_{\mathrm{rel}}^{\min}=10^{-25}\).  The explicit function is given in
    Table~\ref{tab:fixed-params}; it is fixed in the current permeability-focused
    workflow.
\end{itemize}
The remaining unresolved model-provenance items are not equation-formulation issues:
the suspicious active \texttt{CTE} value, the provenance of the open-niche RH pressure
curve, the native-host OGS executable caveat (the collected OGS 6.5.4 SIF is used
through the recorded Dockerized-Apptainer backend), and the still-pending ERT and
Taupe/TDR observation-operator calibrations are tracked in the measurement and workflow
sections.

\section{Model provenance and non-modification constraint}
The editable report folder contains the LaTeX source and a copy of the OGS settings.
For the model audit, the authoritative exchanged inputs are the Gesa TeamBeam archives
copied into
\path{GESA_model_original/2025-04-03_CDA_N4_2D_250403} and
\path{GESA_model_original/2025-05-09_CDA_N4_2D_250509}.
The report's \texttt{ogs\_settings} directory matches the May 2025 XML settings, with the
project file \texttt{cd\_a\_open\_niche\_quad.prj} retained from the April archive.
The April archive also contains the mesh files (\texttt{bulk.vtu}, \texttt{bulk\_all.vtu},
and the boundary meshes), while the May archive updates the timestep/output schedule to
align outputs with monthly ERT data.

The model itself is treated here as frozen. Measurement information should therefore enter
through (i) observation operators applied to the model outputs, (ii) preprocessing of
boundary-condition curves or comparison targets, and (iii) externally generated
parameter-field files or XML parameter replacements used by an inversion workflow.
Those generated fields can vary between inversion samples, but the mathematical meaning
of the OGS process and the original mesh/project structure should remain explicit.

This non-modification claim is also checked by the generated formulation audit
\path{inversion_workflow/ogs_formulation_consistency_audit.md}.  That audit parses the
source XML and the representative run-local XML, verifies 18 formulation checks with
no hard failures, and records the two remaining caveats separately: \texttt{phi} is a
run-local mesh field but fixed at \(0.105\), and the active \texttt{CTE} value still
needs provenance confirmation.  The run-local workflow therefore substitutes
\texttt{k\_i\_rd} for the heterogeneous intrinsic-permeability tensor without changing
the TRM process, phase laws, media laws, or boundary-condition semantics.

\section{Governing equations (Wang 2009 notation)}
Primary variables: displacement \(\uu\), liquid pressure \(\pp\), temperature \(\TT\).
Porous medium: porosity \(\npor\), saturation \(\Sat\), intrinsic permeability \(\kperm\), relative permeability \(\krel\),
liquid density \(\rhoW\), viscosity \(\muW\).

\paragraph{Darcy velocity and mass flux (unsaturated, gravity off):}
The OGS TRM process uses the Darcy velocity
\[
\vW = -\,\frac{\krel\,\kperm}{\muW}\,\grad \pp,
\qquad
\qW = \rhoW\,\vW ,
\]
because \texttt{specific\_body\_force} is zero in \texttt{01\_processes\_TRM.xml}.
The factors \(\npor\Sat\) belong to storage and thermal mixing terms, not to the Darcy
velocity itself \cite[Sec.~``Governing equations without vapor diffusion'']{OpenGeoSysTRMDocs}.

\paragraph{Liquid mass balance (no vapor):}
For the actual OGS TRM formulation without vapor diffusion, the hydraulic equation is
\[
\left(\Sat\beta-\npor\frac{\partial \Sat}{\partial \pcap}\right)\rhoW\,\dot{\pp}
- \Sat\left(
      \frac{\partial \rhoW}{\partial \TT}
      + \rhoW(\alphaB-\Sat)\alpha_T^s
  \right)\dot{\TT}
+ \divv(\rhoW\vW)
+ \Sat\alphaB\rhoW\,\divv\dot{\uu}
= Q_H ,
\qquad \pcap=-\pp .
\]
This resolves the earlier comment on \(\beta_p\): the XML does not use constant density.
The liquid density is the OGS \texttt{Linear} model
\[
\rhoW(\TT,\pp)
=1095\left[1-5\times10^{-4}(\TT-298.15)
+3.2\times10^{-10}(\pp-7.5\times10^6)\right],
\]
so \(\partial\rhoW/\partial\pp\neq0\) and
\(\partial\rhoW/\partial\TT\neq0\).  The OGS storage term is not the informal
\(\Sat\rhoW^{-1}\partial\rhoW/\partial\pp\) expression alone; it is the composite
\(\Sat\beta\) term combined with the capillary-storage term
\(-\npor\,\partial \Sat/\partial \pcap\).  Likewise, vapor diffusion is absent, but
the no-vapor OGS TRM equation still contains a thermal coupling term through liquid
density temperature dependence and solid thermal expansivity
\cite[pp.~1633--1634]{Wang2009THM}
\cite[Sec.~``Governing equations without vapor diffusion'']{OpenGeoSysTRMDocs}.

\paragraph{Momentum balance (quasi-static):}
\[
\divv\!\bigl(\sig - b(\Sat)\alphaB\pp\,\I\bigr)+\bm f=\bm{0},
\qquad
\sig=\bm{C}:\Big(\bm{\varepsilon}(\uu)-\bm{\varepsilon}^{T}
-\bm{\varepsilon}^{\rm sw}(\Sat)\Big).
\]
In this model \(\bm f=\bm0\), \(\alphaB=1\), and
\texttt{BishopsPowerLaw} with exponent \(1\) gives \(b(\Sat)=\Sat\).
The compact form \(\divv(\sig-\Sat\pp\I)=0\) is therefore valid only after those
XML substitutions.  Wang et al. write the thermal stress term directly for an
isotropic special case; OGS instead places thermal strain inside the generalized
Hooke law, which is the correct representation for the configured orthotropic
\texttt{LinearElasticOrthotropic} relation and the active saturation-dependent swelling
term \cite[pp.~1633--1634]{Wang2009THM}
\cite[Sec.~``Governing equations without vapor diffusion'']{OpenGeoSysTRMDocs}.

\paragraph{Heat balance:}
\[
(\rho c_p)^{\rm eff}\dot{\TT}
-\divv\!\left(\bm{k}_T^{\rm eff}\grad\TT\right)
+\rhoW c_w\,\grad\TT\cdot\vW
=Q_T,
\]
with OGS effective phase mixing
\[
(\rho c_p)^{\rm eff}=(1-\npor)\rho_s c_s+\npor\Sat\rhoW c_w,
\qquad
\bm{k}_T^{\rm eff}=(1-\npor)\bm{k}_T^s+\npor\Sat k_T^l\I .
\]
This resolves the heat-balance comment: the missing \(\npor\Sat\) is in storage and
thermal conductivity mixing, while OGS writes the advective heat term with the Darcy
velocity \(\vW\), not with pore velocity. Expanding
\(\divv(\rhoW c_w \vW \TT)\) into \(\rhoW c_w \vW\cdot\grad\TT\) is only valid after
using the mass balance and the OGS weak-form assumptions; for the report we keep the
official OGS form rather than an independently expanded flux form
\cite[Sec.~``Governing equations without vapor diffusion'']{OpenGeoSysTRMDocs}.

\section{What differs from Wang et al. (2009)}
\begin{itemize}[leftmargin=1.2em]
  \item \textbf{Coupling/solver:} one monolithic \texttt{THERMO\_RICHARDS\_MECHANICS}
  process with Backward Euler time discretization and one Newton solver.
  \item \textbf{Gravity:} disabled here (\(\bm g=\bm 0\)); no hydrostatics.
  \item \textbf{Vapor:} neglected here; Wang derives/keeps vapor terms.
  \item \textbf{Elasticity:} orthotropic linear elasticity here vs. isotropic demos in Wang.
  \item \textbf{Bishop/Biot:} \(b(\Sat)=\Sat\) and \(\alpha=1\Rightarrow\) pore-stress term \(\Sat\,\pp\,\I\) (same structure).
  \item \textbf{Swelling:} saturation-dependent swelling strain active here.
  \item \textbf{Thermal conductivity:} OGS effective porosity mixing for \(\keff\) (solid+liquid; no gas).
\end{itemize}

\section{Boundary data}
\begin{itemize}[leftmargin=1.2em]
  \item \textbf{Temperature:} Dirichlet \( \TT=298.15\,\mathrm{K}\) on \texttt{bulk\_all}.
  \item \textbf{Pressure:} Dirichlet \(p=1.5\,\mathrm{MPa}\) on \texttt{cd-a\_top};
  time-dependent \texttt{open\_niche\_seasonal} pressure on \texttt{cd-a\_niche4}.
  The parameter \texttt{bc\_pressure\_outside} is defined but is not attached to an
  active boundary condition.
  \item \textbf{Mechanics:} zero normal displacement on the outer box
  (\texttt{left/right} in component 0, \texttt{top/bottom} in component 1).
  \texttt{load\_top} and \texttt{initial\_stress} are defined/commented but inactive.
\end{itemize}

\section{XML \texorpdfstring{$\rightarrow$}{->} PDE symbol mapping}
Below, each XML entry is mapped to the PDEs parameter.
% ===== TABLE A: Medium & phases =====
\begin{longtable}{P{4.5cm} P{2cm} P{1.5cm} P{2cm} P{7cm}}
\caption{Medium/phases: properties and laws mapped to PDE symbols}
\label{tab:medium-mapping}\\
\toprule
\textbf{XML path (name)} & \textbf{Type} & \textbf{Symbol} & \textbf{Unit} & \textbf{Where it appears / comment} \\
\midrule
\endfirsthead
\caption[]{Medium/phases: properties and laws mapped to PDE symbols (continued)}\\
\toprule
\textbf{XML path (name)} & \textbf{Type} & \textbf{Symbol} & \textbf{Unit} & \textbf{Where it appears / comment} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\emph{Continued on next page}}\\
\midrule
\endfoot
\bottomrule
\endlastfoot
\texttt{porosity (phi)} & Parameter & \(\npor\) & -- &
Storage in mass balance; mixing in thermal storage/conductivity. \\
\texttt{permeability (k\_i)} & Param (tensor) & \(\kperm\) & m\(^2\) &
Darcy flux; anisotropy allowed. \\
\texttt{biot\_coefficient (biot)} & Parameter & \(\alpha\) & -- &
Pore-stress partition (with Bishop \(b(\Sat)=\Sat\)). \\
\texttt{thermal\_conductivity (mixing)} & Model & \(\keff\) & W\,m\(^{-1}\)K\(^{-1}\) &
Conductive heat flux; porosity mix of solid+liquid. \\
\texttt{viscosity (eta)} & Parameter & \(\muW\) & Pa\,s &
Flow resistance in Darcy’s law. \\
\texttt{density (Linear)} & Model & \(\rhoW(\TT,\pp)\) & kg\,m\(^{-3}\) &
Storage/advection terms; linearized about a reference state. \\
\texttt{specific\_heat\_capacity (c\_p\_l)} & Parameter & \(c_w\) & J\,kg\(^{-1}\)K\(^{-1}\) &
Enters \(\Ceff\) and heat advection. \\
\texttt{thermal\_conductivity (kappa\_l)} & Parameter & \(k_\ell\) & W\,m\(^{-1}\)K\(^{-1}\) &
Input to the effective \(\keff\) mixing. \\
\texttt{density (rho\_s)} & Parameter & \(\rho_s\) & kg\,m\(^{-3}\) &
Thermal storage mixing (solid fraction). \\
\texttt{specific\_heat\_capacity (c\_p\_s)} & Parameter & \(c_s\) & J\,kg\(^{-1}\)K\(^{-1}\) &
Thermal storage mixing (solid fraction). \\
\texttt{thermal\_conductivity (kappa\_th\_s)} & Parameter & \(k_s\) & W\,m\(^{-1}\)K\(^{-1}\) &
Input to effective \(\keff\). \\
\texttt{thermal\_expansivity (CTE)} & Parameter & \(\alpha_T\) & K\(^{-1}\) &
Thermal strain and hydraulic thermal-storage coupling; the active XML value is suspicious and must not be interpreted as calibrated. \\
\texttt{swelling\_stress\_rate} & Model & \(\bm{\varepsilon}^{\rm sw}(\Sat)\) & -- &
Saturation-dependent swelling strain (isotropic; limits in XML). \\
\path{relative_permeability} (VG) & Model & \(k_{\mathrm{rel}}\) & -- &
Hydraulic conductivity factor in Darcy’s law. \\
\texttt{saturation (VG)} & Model & \(\Sat(\pp_c)\) & -- &
Storage term via \(\partial \Sat/\partial \pp\). \\
\texttt{bishops\_effective\_stress (power=1)} & Model & \(b(\Sat)=\Sat\) & -- &
Pore-stress scaling in momentum balance. \\
\end{longtable}
% ===== TABLE B: ICs/BCs =====
\begin{longtable}{P{4cm} P{2cm} P{1.5cm} P{3.5cm} P{5cm}}
\caption{ICs/BCs: parameters mapped to variables and equations}
\label{tab:icbc-mapping}\\
\toprule
\textbf{XML path (name)} & \textbf{Type} & \textbf{Applies to} & \textbf{Unit} & \textbf{Meaning / where used} \\
\midrule
\endfirsthead
\caption[]{ICs/BCs: parameters mapped to variables and equations (continued)}\\
\toprule
\textbf{XML path (name)} & \textbf{Type} & \textbf{Applies to} & \textbf{Unit} & \textbf{Meaning / where used} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\emph{Continued on next page}}\\
\midrule
\endfoot
\bottomrule
\endlastfoot
\texttt{ic\_displacement} & Constant & \(\uu(\cdot,0)\) & m &
Initial displacement (typically \(\bm 0\)). \\
\texttt{ic\_pressure} & Function & \(\pp(\cdot,0)\) & Pa &
Initial liquid pressure (current function yields a constant). \\
\texttt{ic\_temperature} & Constant & \(\TT(\cdot,0)\) & K &
Initial temperature. \\
\texttt{bc\_displacement} & Constant & \(\uu\) & m &
Zero-displacement box (kinematic constraints). \\
\texttt{bc\_top\_pressure} & Function & \(\pp\) & Pa &
Dirichlet pressure on top boundary. \\
\texttt{open\_niche\_seasonal} & CurveScaled & \(\pp\) & Pa &
Time-varying pressure on niche boundary. \\
\texttt{bc\_temperature\_outside} & Constant & \(\TT\) & K &
Outer temperature Dirichlet. \\
\texttt{load\_top} & Function & traction & Pa &
Defined but inactive in the process file. \\
\texttt{bc\_atm\_pressure} & Constant & ref. & Pa &
Reference value; not bound to an active BC. \\
\end{longtable}

\section{Model parameters, fixed values and candidate priors}
\label{sec:params-and-priors}

In this section we collect all material parameters entering the TRM model and split
them into: (i) parameters and constitutive laws that are kept fixed from the exchanged
model for the present workflow, and (ii) parameters that could be released in a later
Bayesian calibration once the relevant observation operators are active.  The only
implemented field unknown at present is the intrinsic permeability tensor
\(\kperm(\bm x)\), treated through run-local mesh-cell data.  The sampled NMR state
residual is now part of the active objective, but porosity remains a fixed support
field until the NMR residual policy and porosity--saturation separation gate are
approved.  Retention and mechanical parameters are listed as later candidate priors,
not as already-fitted active unknowns.  The machine-readable staging decision is regenerated by
\path{inversion_workflow/scripts/build_inversion_parameter_release_plan.py} and stored
in \path{inversion_workflow/inversion_parameter_release_plan.md}.

% ============================================================
% FIXED PARAMETERS
% ============================================================
\begin{longtable}{P{3.8cm} P{1.8cm} P{2.6cm} P{8.7cm}}
\caption{Fixed material and fluid parameters and constitutive laws (values taken from the XML configuration).}
\label{tab:fixed-params}\\
\toprule
\textbf{XML name / property} & \textbf{Symbol} & \textbf{Unit} & \textbf{Value / definition}\\
\midrule
\endfirsthead
\caption[]{Fixed material and fluid parameters and constitutive laws (continued).}\\
\toprule
\textbf{XML name / property} & \textbf{Symbol} & \textbf{Unit} & \textbf{Value / definition}\\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{\emph{Continued on next page}}\\
\midrule
\endfoot
\bottomrule
\endlastfoot

\multicolumn{4}{l}{\emph{Solid phase (Opalinus Clay matrix)}}\\
\midrule
\texttt{rho\_s} (density) & \(\rho_s\) & kg\,m\(^{-3}\) &
Dry solid density, taken constant:
\(\rho_s = 2.52\times 10^3\).\\

\texttt{kappa\_th\_s} (thermal\_conductivity) & \(k_s\) & W\,m\(^{-1}\)K\(^{-1}\) &
Solid thermal conductivity:
\(k_s = 2.156\).\\

\texttt{c\_p\_s} (specific\_heat\_capacity) & \(c_s\) & J\,kg\(^{-1}\)K\(^{-1}\) &
Solid specific heat capacity:
\(c_s = 1254.74\).\\

\texttt{CTE} (thermal\_expansivity) & \(\alpha_T\) & K\(^{-1}\) &
Active XML value
\(\alpha_T = 1.25474\times 10^3\), with the XML comment incorrectly labelling it
as a heat-capacity-like unit. This is not physically plausible for a rock thermal
expansion coefficient and is likely a copied placeholder from \texttt{c\_p\_s}.
The generated thermal-expansivity audit compares this value with HE-D/Opalinus Clay
reference scales: Garitte et al. list linear solid thermal-expansion coefficients
from \(1.0\times10^{-5}\) to \(2.6\times10^{-5}\,\mathrm{K^{-1}}\), and Gens et al.
used \(1.4\times10^{-5}\,\mathrm{K^{-1}}\) in thermal-loading interpretation
\cite[PDF p.~12]{Garitte2017}\cite[PDF p.~14]{Gens2017}.  The XML value is therefore
\(4.83\times10^7\) times the high end of that range.  Because the current run is
nearly isothermal, the hydraulic calibration can proceed only if this parameter is
treated as an active-model caveat, not as a calibrated Opalinus Clay property.\\

\texttt{swelling\_stress\_rate} (SaturationDependentSwelling) &
\(\bm{\varepsilon}^{\mathrm{sw}}(S)\) & -- &
Isotropic saturation-dependent swelling strain defined by the OGS
\texttt{SaturationDependentSwelling} model with
swelling pressures \(p_{\mathrm{sw}} = 1.0\times10^6\)~Pa in all principal directions,
exponents \(1,1,1\),
and activation for \(S\in[0.1,1]\).
The detailed functional form is kept fixed as in the XML.\\

\texttt{E}, \texttt{G}, \texttt{nu} (orthotropic elasticity) &
\(\bm{C}\) & Pa, -- &
Orthotropic linear elasticity as in \texttt{LinearElasticOrthotropic}:
Young moduli
\(E_1 = 13.8\times10^9\)~Pa,
\(E_2 = 6.0\times10^9\)~Pa,
\(E_3 = 13.8\times10^9\)~Pa;
shear moduli
\(G_1 = 4.79\times10^9\)~Pa,
\(G_2 = 2.46\times10^9\)~Pa,
\(G_3 = 4.79\times10^9\)~Pa;
Poisson ratios
\(\nu_{12} = 0.44\),
\(\nu_{23} = 0.22\),
\(\nu_{13} = 0.44\).
These are kept fixed in the hydraulic-focused inversion.\\[0.3em]

\multicolumn{4}{l}{\emph{Liquid phase (aqueous pore water)}}\\
\midrule
\texttt{c\_p\_l} (specific\_heat\_capacity) & \(c_w\) & J\,kg\(^{-1}\)K\(^{-1}\) &
Liquid specific heat capacity:
\(c_w = 4160\).\\

\texttt{kappa\_l} (thermal\_conductivity) & \(k_\ell\) & W\,m\(^{-1}\)K\(^{-1}\) &
Liquid thermal conductivity:
\(k_\ell = 0.6\).\\

\texttt{eta} (viscosity) & \(\mu_w\) & Pa\,s &
Dynamic viscosity of the liquid:
\(\mu_w = 1.0\times 10^{-3}\), constant (temperature dependence neglected in this configuration).\\

\texttt{density} (Linear) & \(\rho_w(T,p)\) & kg\,m\(^{-3}\) &
Liquid density given by an affine law in temperature and pressure:
\[
\rho_w(T,p)
= \rho_{w,0}\Bigl(1
+ a_T\,(T-T_0)
+ a_p\,(p-p_0)\Bigr),
\]
with reference value \(\rho_{w,0} = 1095\),
\(T_0 = 298.15\)~K,
\(p_0 = 7.5\times10^6\)~Pa,
and slopes
\(a_T = -5\times10^{-4}\,\mathrm{K}^{-1}\),
\(a_p = 3.2\times10^{-10}\,\mathrm{Pa}^{-1}\).\\[0.3em]

\multicolumn{4}{l}{\emph{Medium-scale thermal mixing}}\\
\midrule
\texttt{thermal\_conductivity} (EffectiveThermalConductivityPorosityMixing) &
\(k_{\mathrm{eff}}(S)\) & W\,m\(^{-1}\)K\(^{-1}\) &
Effective thermal conductivity of the porous medium, with liquid and solid only
(gas neglected):
\[
k_{\mathrm{eff}}(S)
= n S\,k_\ell + (1-n)\,k_s.
\]
The porosity \(n\) is given below, and \(k_\ell, k_s\) are as above.\\[0.3em]

\multicolumn{4}{l}{\emph{Hydraulic constitutive laws (van Genuchten)}}\\
\midrule
\path{relative_permeability} (RelativePermeabilityVanGenuchten) &
\(k_{\mathrm{rel}}(S)\) & -- &
van Genuchten--Mualem relative permeability function with residual saturations
\(S_{\ell r} = 0.1\), \(S_{gr}=0\),
exponent \(m = 0.45\),
and minimum liquid relative permeability
\(k_{\mathrm{rel}}^{\min} = 10^{-25}\):
\[
\begin{aligned}
S_e &=
\frac{S_\ell - S_{\ell r}}{1 - S_{\ell r} - S_{gr}},\\
k_{\mathrm{rel}}(S_\ell)
&= S_e^{1/2}
\Bigl[1-\bigl(1 - S_e^{1/m}\bigr)^m\Bigr]^2.
\end{aligned}
\]
Here \(S_\ell\) is the liquid saturation.\\

\texttt{saturation} (SaturationVanGenuchten) &
\(S_\ell(p_c)\) & -- &
Water-retention curve (drying branch) in van Genuchten form with
\(S_{\ell r} = 0.1\), \(S_{gr} = 0\),
exponent \(m = 0.45\)
and air-entry pressure \(p_b = 10\,\mathrm{MPa}\):
\[
S_\ell(p_c)
= S_{\ell r}
+ (1-S_{\ell r}-S_{gr})
\Bigl[1 + \bigl(\tfrac{p_c}{p_b}\bigr)^{1/(1-m)}\Bigr]^{-m},
\]
where \(p_c\) is the capillary pressure.\\

\path{bishops_effective_stress} (BishopsPowerLaw) &
\(b(S)\) & -- &
Bishop effective-stress function
\(b(S) = S^q\) with exponent \(q=1\),
i.e. \(b(S) = S\).\\[0.3em]

\multicolumn{4}{l}{\emph{Poromechanical coupling and porosity (fixed in this study)}}\\
\midrule
\texttt{phi} (porosity) & \(n\) & -- &
Total (water-loss) porosity used in the Richards and thermal mixing terms:
\[
n = 0.105.
\]
In the present configuration this value is taken as fixed and is only used as a reference for the prior in Table~\ref{tab:inv-params}.\\

\texttt{biot} (biot\_coefficient) & \(\alpha\) & -- &
Biot coefficient, here fixed to
\(\alpha = 1.0\).\\

\end{longtable}

% ============================================================
% INVERSION PARAMETERS
% ============================================================
\begin{longtable}{P{3.0cm} P{3.0cm} P{4.7cm} P{6.3cm}}
\caption{Candidate hydraulic parameters and prior distributions for staged Bayesian calibration.  Only the intrinsic permeability tensor field is implemented in the current workflow; scalar porosity and retention parameters should be released only after OGS state-output residuals are active.}
\label{tab:inv-params}\\
\toprule
\textbf{Parameter / function} & \textbf{XML reference value} & \textbf{Prior distribution} & \textbf{Role if released}\\
\midrule
\endfirsthead
\caption[]{Candidate hydraulic parameters and prior distributions for staged Bayesian calibration (continued).}\\
\toprule
\textbf{Parameter / function} & \textbf{XML reference value} & \textbf{Prior distribution} & \textbf{Role if released}\\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{\emph{Continued on next page}}\\
\midrule
\endfoot
\bottomrule
\endlastfoot

\multicolumn{4}{l}{\emph{Porosity and water-retention curve (later-release scalar parameters)}}\\
\midrule
Porosity of Opalinus Clay &
\(n_0 = 0.105\) &
Normal:
\(\displaystyle n \sim \mathcal{N}(0.105,\;0.02^2)\) &
Scalar porosity controlling storage and thermal mixing.
Mean set to the XML value,
standard deviation chosen to cover the range
\(n\approx 0.09\)--0.17 reported for Mont Terri OPA:
Nagra diffusion and rock-capacity data give HTO-accessible porosities
of about 0.14--0.17, with some method- and tracer-specific values
around 0.09--0.11
\cite[pp.~26--27, Tables~8--9 and pp.~44, 65--66, Tables~12 and 19]{VanLoon2004Nagra},
while the geomechanical compilation reports total porosity values in the
same order \cite[pp.~153--156]{Amann2015}).\\

van Genuchten exponent (retention) \(m\) &
\(m_0 = 0.45\) &
Normal:
\(\displaystyle m \sim \mathcal{N}(0.45,\;0.05^2)\) &
Scalar shape parameter of the water-retention curve.
The mean is the XML value, consistent with laboratory WRC fits
for Opalinus Clay where \(m\) typically lies in the range
\(0.4\)–\(0.6\) depending on facies and stress path
\cite[pp.~22--30, Sect.~4]{VillarRomero2012}.\\

Air-entry pressure \(p_b\) in VG WRC &
\(p_{b,0} = 10~\mathrm{MPa}\) &
Uniform:
\(\displaystyle p_b \sim \mathcal{U}(5\,\mathrm{MPa},\,20\,\mathrm{MPa})\) &
Controls the suction range over which desaturation occurs.
The XML value \(10\)~MPa is taken as central;
the bounds reflect roughly a factor-two scatter reported in
fitted WRCs for OPA under different conditions
(e.g. \cite[pp.~31--33, Sect.~5]{VillarRomero2012} and
\cite[p.~4448]{WaterContentEDZ2024}).\\[0.3em]

\multicolumn{4}{l}{\emph{Intrinsic permeability tensor (random field + global anisotropy)}}\\
\midrule
Permeability magnitude (log-field) &
\(\begin{aligned}
k_x&=1.00\times10^{-19}\\
k_y&=4.00\times10^{-20}\\
k_{\mathrm{ref}}&=6.32\times10^{-20}
\end{aligned}\)
\(\mathrm{m}^2\)
&
Lognormal RF:
\(\ln k_{\mathrm{mag}}\sim \mathcal{N}(\mu_k,\sigma_k^2)\).
\(\mu_k = \ln(6.32\times10^{-20})\);
\(\sigma_k = 0.5\).
The prior generator draws this field independently of \(\bm x\) before spatial
correlation is imposed. &
Scalar permeability magnitude field entering the intrinsic permeability tensor
\(\bm{k}_{\mathrm{perm}}(\bm x)\).
The mean is chosen as the geometric mean of the XML principal values
\(1.00\times10^{-19}\) and \(4.00\times10^{-20}\,\mathrm{m}^2\);
\(\sigma_k = 0.5\) (natural-log scale) corresponds to an order-of-magnitude prior range
consistent with OPA hydraulic characterisations
\cite[pp.~130--135]{Marschall2005}
\cite[pp.~3--5]{Garitte2017}
\cite[pp.~223--227]{ComparativeHydraulicOPA2017}
\cite[pp.~4450--4452]{WaterContentEDZ2024}.\\

Global anisotropy ratio \(r = k_{\parallel}/k_{\perp}\) &
\(\begin{aligned}
k_x&=1.00\times10^{-19}\\
k_y&=4.00\times10^{-20}\\
r_0&=2.5
\end{aligned}\)
&
Lognormal (scalar):
\(\ln r \sim \mathcal{N}(\mu_r,\sigma_r^2)\).
\(\mu_r = \ln(2.5)\);
\(\sigma_r = 0.4\).
&
Global (spatially constant) anisotropy ratio between
the permeability components parallel and normal to bedding.
The prior mean reproduces the XML ratio; the chosen \(\sigma_r\) allows
\(r\) in the interval of a few to about ten, which is compatible with
directional anisotropies reported for Opalinus Clay
\cite[pp.~130--135]{Marschall2005}
\cite[pp.~225--227]{ComparativeHydraulicOPA2017}.\\

Global bedding-orientation angle \(\theta\) in the tunnel cross-section &
The current XML tensor \(\texttt{k\_i}\) is aligned with the global axes,
which we interpret as a reference angle
\[
\theta_0 = 0~\text{rad}
\]
&
Normal (scalar):
\[
\theta \sim \mathcal{N}\bigl(0,\sigma_\theta^2\bigr),
\qquad
\sigma_\theta = \pi/12,
\]
i.e. a standard deviation of \(15^\circ\). &
Global (spatially constant) rotation of the intrinsic permeability tensor
in the tunnel cross-section.
The prior mean corresponds to the current XML configuration (no rotation);
\(\sigma_\theta = 15^\circ\) reflects moderate uncertainty in the effective
alignment of hydraulic anisotropy with the structural bedding orientation
as inferred from geological and geophysical observations
\cite[pp.~130--135]{Marschall2005}
\cite[pp.~2--5]{Garitte2017}
\cite[pp.~4447--4450]{WaterContentEDZ2024}.\\

\end{longtable}

In summary, the fixed set (Table~\ref{tab:fixed-params}) contains thermal properties,
fluid properties, the Biot coefficient, the Bishop function, the detailed form of the
saturation-dependent swelling strain, and the orthotropic elastic constants, which are
constrained independently by thermal and mechanical experiments on Opalinus Clay
(e.g.~heating tests HE-B/HE-D/HE-E and geomechanical campaigns
\cite[pp.~270--279]{Gens2017} \cite[pp.~153--166]{Amann2015}
\cite[pp.~211--222]{ThermalEffectsOPA2010}).

The staged Bayesian workflow should start with the intrinsic permeability tensor
\(\bm{k}_{\mathrm{perm}}\) because it is the only parameter field with a direct
measurement target layer in the current files.  It is parameterised as
\[
\bm{k}_{\mathrm{perm}}(\bm x)
= k_{\mathrm{mag}}(\bm x)\,
\mathbf{R}(\theta)^\top
\begin{pmatrix}
r & 0\\[0.3em]
0 & 1
\end{pmatrix}
\mathbf{R}(\theta),
\]
where \(k_{\mathrm{mag}}(\bm x)\) is a lognormal scalar random field and
\(r\) and \(\theta\) are global (spatially constant) scalar parameters describing,
respectively, the anisotropy ratio and the bedding-related orientation of the tensor.
This reflects the empirical evidence that permeability magnitudes in Opalinus Clay
vary by roughly one to two orders of magnitude at the metre scale and that the
principal directions of anisotropy are controlled by the large-scale bedding fabric
and can be treated as homogeneous at the tunnel scale
\cite[pp.~130--135]{Marschall2005}
\cite[pp.~2--5]{Garitte2017}
\cite[pp.~225--227]{ComparativeHydraulicOPA2017}
\cite[pp.~4447--4450]{WaterContentEDZ2024}.
The Gaussian priors for \(n\) and \(m\), and the uniform prior for \(p_b\), are retained
as later scalar release options.  They are centred at or around the XML values, which
are themselves consistent with independent porosity and WRC measurements for Mont
Terri samples
\cite[pp.~44 and 65--66, Tables~12 and 19]{VanLoon2004Nagra}
\cite[pp.~22--33, Sects.~4--5]{VillarRomero2012}.  They should remain fixed in the
first production inversion unless NMR, ERT, RH, and Taupe/TDR state residuals show that
permeability alone cannot explain the hydraulic evolution.


\input{measurement_chapter}

\section{Full XML listings}

\subsection*{04\_media\_TRM.xml}
\lstinputlisting[style=xml]{ogs_settings/04_media_TRM.xml}

\subsection*{04\_1\_media\_aqu\_liq.xml}
\lstinputlisting[style=xml]{ogs_settings/04_1_media_aqu_liq.xml}

\subsection*{04\_2\_media\_xml}
\lstinputlisting[style=xml]{ogs_settings/04_2_media_twophase.xml}

\subsection*{03\_parameters\_TRM.xml}
\lstinputlisting[style=xml]{ogs_settings/03_parameters_TRM.xml}

\bibliographystyle{amsplain}
\bibliography{opalinus_clay}

\end{document}
